Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-12 paper.tex
Note that peak C_T method is not restricted to standard symmetrical airfoils; resolves #68
Text wrapping
Define Re in terms of Fr; resolves #62

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important nondimensional parameter is often the Reynolds number, $Re$, which
quantifies the importance of inertial forces over viscous forces on the flow
physics:
\begin{equation}
    Re = \frac{Ul}{\nu},
    \label{eq:Re}
\end{equation}
where $U$ and $l$ are characteristic velocity and length scales, respectively,
and $\nu$ is the fluid kinematic viscosity. In general the geometric scale of a
physical model is not necessarily the same as its dynamical scale. As such,
hereafter we will use the word ``scale'' to refer to this dynamical scale or
Reynolds number.

@@

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity---a better predictor than conventional
quantifications of airfoil performance, e.g., lift-to-drag ratio. The simple
peak geometric torque coefficient model predicted Reynolds number independence
for Reynolds numbers based on blade chord of $Re_c > 2 \times 10^5$. Is it also
shown from this metric that foils with higher camber are more Reynolds number
dependent at lower Reynolds number but have smaller slopes in the linear regime.
The Reynolds number dependence of the peak torque coefficient calculated from
static foil data and cross-flow turbine kinematics was shown to be a reasonable
indicator for predicting Reynolds number dependence of an actual cross-flow
turbine operating under dynamic conditions, including dynamic stall.

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical if certain nondimensional physical
parameters are matched. In the case of fluid systems, the most important
nondimensional parameter is often the Reynolds number, $Re$, which quantifies
the importance of inertial forces over viscous forces on the flow physics: $Re
\equiv Ul/\nu$, where $U$ and $l$ are characteristic velocity and length scales,
respectively, and $\nu$ is the fluid kinematic viscosity. The other common
dynamical scale---for systems with a free surface---is the Froude number $Fr
\equiv U/\sqrt{gl}$, where $g$ is the gravitational acceleration. Matching both
Froude and Reynolds number is difficult for the same fluid, which is illustrated
by the relation $Re = l^{3/2} g^{1/2} Fr / \nu$, since $Re$ scales linearly with
$l$, or the geometric scale. In general the geometric scale of a physical model
is not necessarily the same as its dynamical scale. As such, hereafter we will
use the word ``scale'' to refer to this dynamical scale or Reynolds number and
assume Froude number is small enough to be negligible.

@@

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity---a better predictor than conventional
quantifications of airfoil performance, e.g., lift-to-drag ratio. Note that this
method is not restricted to standard symmetrical NACA foils. The simple peak
geometric torque coefficient model predicted Reynolds number independence for
Reynolds numbers based on blade chord of $Re_c > 2 \times 10^5$. Is it also
shown from this metric that foils with higher camber are more Reynolds number
dependent at lower Reynolds number but have smaller slopes in the linear regime.
The Reynolds number dependence of the peak torque coefficient calculated from
static foil data and cross-flow turbine kinematics was shown to be a reasonable
indicator for predicting Reynolds number dependence of an actual cross-flow
turbine operating under dynamic conditions, including dynamic stall.
